---
engine: knitr
---

# Code

You can include various code blocks.
We'll demonstrate with R code initially.

## Inline code

You can include inline code.

This sentence ends with a number created by inline code, 1+1 = `r 1+1`.

The above sentence in markdown code:

````{verbatim}
This sentence ends with a number created by inline code, 1+1 = `r 1+1`.
````

## Code block

Code block and output:

```{r}
1+1
```

Code block markdown code:

````{verbatim}
```{r}
1+1
```
````

## Display code block

To show the code block but not the output add the option `eval=FALSE`

```{r, eval=FALSE}
#Below is some example code that we don't want markdown/quarto to run
#We just want the code block to be displayed
long_function(x=long_data, y=more_data)
```

Code block markdown code:

````{verbatim}
```{r, eval=FALSE}
#Below is some example code that we don't want markdown/quarto to run
#We just want the code block to be displayed
long_function(x=long_data, y=more_data)
```
````

## Display output

To show only the output but not the code block add the option `echo=FALSE`

```{r, echo=FALSE}
100*12
```

Code block markdown code:

````{verbatim}
```{r, echo=FALSE}
100*12
```
````

## Libraries

Libraries need to be loaded for each page you want to use them.

You can add the below code block at the top of your markdown page to silently load the `Tidyverse` package.
Otherwise your markdown file will have all the unneeded output from loading a library.

````{verbatim}
```{r, echo=FALSE, warning=FALSE, results=FALSE, output=FALSE}
#Load library so functions run smoothly
library(tidyverse)
```
````

## Non R code

You can include bash and python code.

### Python

Python code:

```{python, eval=FALSE}
1+1
```

Markdown code:

````{verbatim}
```{python, eval=FALSE}
1+1
```
````

More information include installation instructions here: [Quarto Using Python](https://quarto.org/docs/computations/python.html)

### Bash/Linux

Linux code:

```{bash,eval=FALSE}
cd ~/project_dir/analysis_1
```

````{verbatim}
```{bash,eval=FALSE}
cd ~/project_dir/analysis_1
```
````

### Force knitr engine

If your page has no R code and uses non-R languages you will need the below code at the top of each `.qmd` page that contains non R code.
This will mean you will still produce `.html` pages.
You need this even if you set `eval=FALSE`.

```{bash, eval=FALSE}
---
engine: knitr
---
```

## Verbatim

You can display the markdown code for a code block.

Code block:

```{r}
1+1
```

Markdown code for code block:

````{verbatim}
```{r}
1+1
```
````

Markdown code for code block's markdown code:

`````{verbatim}
````{verbatim}
```{r, eval=TRUE}
1 + 1
```
````
`````

::: {.callout-note collapse="true" title="Verbatim a verbatim"}
If you want to verbatim a verbatim you'll need to add an extra back tick (`).

Markdown code for last verbatim code:

``````{verbatim}
`````{verbatim}
````{verbatim}
```{r, eval=TRUE}
1 + 1
```
````
`````
``````
:::

