---
engine: knitr
---
```{r, echo=FALSE, warning=FALSE, results=FALSE, output=FALSE}
library("icons")
```

# Icons

You can use Icons in your bookdown

Package site: [https://github.com/mitchelloharawild/icons](https://github.com/mitchelloharawild/icons)

::: {.callout-note}
You will only be able to use free icons.
:::

## Fontawesome

Generally FOnt awesome is my first choice for most icons.

The below code can be used to add `r icons::icon_style(icons::fontawesome("rocket", style="solid"), fill = "#648fff")`. Colour chosen to work on Light and Dark styles.

````{verbatim}
`r icons::icon_style(icons::fontawesome("rocket", style="solid"), fill = "#648fff")`
````

To add to text do like so:

````{verbatim}
A compass 
(`r icons::icon_style(icons::fontawesome("compass", style="solid"), fill = "#648fff")`) 
is useful to find north.
````

This will produce:

A compass 
(`r icons::icon_style(icons::fontawesome("compass", style="solid"), fill = "#648fff")`)
is useful to find north.

::: {.callout-note}
You need to set the style fontawesome but not the below 2 icon sets.
More info below in the [Searching part](#searching) and [Fontawesome styles](#fontawesome-styles).
:::

## Ionicons

Ionicons is my second choice.

The below code can be used to add `r icons::icon_style(icons::ionicons("calculator"), fill = "#648fff")`.

````{verbatim}
`r icons::icon_style(icons::ionicons("calculator"), fill = "#648fff")`
````

## Bioicons

Bioicons is good for biological icons.

The below code can be used to add `r icons::bioicons("dna-7")`.

````{verbatim}
`r icons::bioicons("dna-7")`
````

## Searching

Search for your icons via the following websites:

- [Fontawesome](https://fontawesome.com/search)
- [Ionicons](https://ionic.io/ionicons)
- [Bioicons](https://bioicons.com/)

You can check if the name will work with:

```{r, eval=TRUE}
icons::icon_find("rocket")
```

You get a bunch of text but the important lines are:

````{verbatim}
$`ionicons$rocket`
````

and

````{verbatim}
$`fontawesome$solid$rocket`
````

This shows there is a rocket icon in ionicons and fontawesome.

Let's display them.

**Ionicons:**

`r icons::icon_style(icons::ionicons("rocket"), fill = "#648fff")`

Code:

````{verbatim}
`r icons::icon_style(icons::ionicons("rocket"), fill = "#648fff")`
````

**Fontawesome:**

`r icons::icon_style(icons::fontawesome("rocket", style="solid"), fill = "#648fff")`

Code:

````{verbatim}
`r icons::icon_style(icons::fontawesome("rocket", style="solid"), fill = "#648fff")`
````

## Fontawesome styles

Notice in the search line for fontawesome we had the style (`solid`) between the set (`fontawesome`) and the icon (`rocket`).
This is because fontawesome will have some icons with multiple styles.
An example is circle.

```{r, eval=TRUE}
icons::icon_find("circle")
```

We can display the solid and regular circle for fontawesome.

**Solid circle:**

`r icons::icon_style(icons::fontawesome("circle", style="solid"), fill = "#648fff")`

Code:

````{verbatim}
`r icons::icon_style(icons::fontawesome("circle", style="solid"), fill = "#648fff")`
````

**regular circle:**

`r icons::icon_style(icons::fontawesome("circle", style="regular"), fill = "#648fff")`

Code:

````{verbatim}
`r icons::icon_style(icons::fontawesome("circle", style="regular"), fill = "#648fff")`
````

## Installing icons

See install and icon set download instructions in the [setup page](/setup/setup.qmd#r-package-installs). 