# Tables

You can include tables.

## Handmade

The easiest way to create a table in VScode is to:

1.  **Enter visual mode:** Right click on markdown page and select `Edit in Visual mode`
2.  Click the `Table` option in the top menu of the page
3.  Click `Insert Table`
4.  Choose your preferred options followed by `OK`
5.  Fill in your table

Example table:

| qmd           | css                                        | yml           |
|---------------|--------------------------------------------|---------------|
| contents      | theme                                      | structure     |
| lots of files | one dark and one light file and maybe more | one main file |
| Markdown code | scss and css code                          | quarto        |

## R table

You can also display R `data.frames` and matrices.
I like to use the [`reactable` package](https://glin.github.io/reactable/index.html).

```{r}
#Load package
library("mgrtibbles")
#Set seed for random sampling
set.seed("483")
#mushroom_tbl tibble for demonstration
mushroom_tbl <- mgrtibbles::mushroom_tbl |>
    #Random sample of 150 rows
    dplyr::slice_sample(n = 150, replace=FALSE)
#Reset random seed to normal operation
set.seed(NULL)
```

```{r}
library("reactable")
options(reactable.theme = reactableTheme(
  color = "hsl(233, 9%, 87%)",
  backgroundColor = "hsl(233, 9%, 19%)",
  borderColor = "hsl(233, 9%, 22%)",
  stripedColor = "hsl(233, 12%, 22%)",
  highlightColor = "hsl(233, 12%, 24%)",
  inputStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  selectStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  pageButtonHoverStyle = list(backgroundColor = "hsl(233, 9%, 25%)"),
  pageButtonActiveStyle = list(backgroundColor = "hsl(233, 9%, 28%)")
))
mushroom_tbl |>
    reactable::reactable()
```