# Webexercises

[`webexercises`](https://debruine.github.io/webexercises/) is an R package that allows you to include interactive quizzes in quarto markdown (`.qmd`) and R markdown (`.rmd`) created html pages. 

## Install

Install through R with:

```{r, eval=FALSE}
install.packages("webexercises")
```

## Initialise

Open the main directory of your quarto site (directory that contains the `index.qmd` and `_quarto.yml`).
Run the following command in an R terminal:

```{r, eval=FALSE}
library("webexercises")
webexercises::add_to_quarto()
```

This will add the following:

A `webex.css` and `webex.js` in an include directory.
For a nice MCQ presentation i change the `.webex-radiogroup label` in `webex.css` to:

```{bash, eval=FALSE}
.webex-radiogroup label {
  /*Text colour*/
  color: : #aaaaaa;
  margin-left: 2em;
  margin-bottom: 0.25em;
  text-indent: -1em;
  padding-left: 0.5em;
  font-weight: 400;
  display: block;
  /*Set border of text to solid and dark grey*/
  border: 2px solid #808080;
  border-radius: 0.25em;
}
```

Additionally, a `webexercises.qmd` file is created.
This contains examples of the various different quizzes.
I delete this.