# Webexercises

[`webexercises`](https://debruine.github.io/webexercises/) is an R package that allows you to include interactive quizzes in quarto markdown (`.qmd`) and R markdown (`.Rmd`) created html pages. 

This page includes:

- MCQ examples & template
- Expandable box example/template
- Installation
- Initialisation for your quarto project

There are other widgets that I don't find use for in the [webexercises website](https://psyteachr.github.io/webexercises/articles/webexercises.html).

# MCQs

## Example

MCQ:

```{r, echo = FALSE}
opts_p <- c("**A1**", "**A2**", answer="**A3**")
```
1. Question? `r longmcq(opts_p)`

Code:

````{verbatim}
```{r, echo = FALSE}
opts_p <- c("**A1**", "**A2**", answer="**A3**")
```
1. Question? `r longmcq(opts_p)`
````

## template

````{verbatim}
```{r, echo = FALSE}
opts_p <- c("** **", "** **", "** **")
```
`r longmcq(opts_p)`
````

## Expandable box

Expandable box:

`r hide("Title")` Contents `r unhide()`

Code:

```{r, eval=FALSE}
`r hide("Title")`
Contents
`r unhide()`
```

Optionally, you may want to use a [callout block](/qmds/callouts.qmd).

::: {.callout-note collapse="true" title="Title"}
Contents
:::

```{bash,eval=FALSE}
::: {.callout-note collapse="true" title="Title"}
Contents
:::
```

## Install

See install instruction in the [setup page](/setup/setup.qmd#r-package-installs). 

## Initialise

Open the main directory of your quarto site (directory that contains the `index.qmd` and `_quarto.yml`).
Run the following command in an R terminal:

```{r, eval=FALSE}
library("webexercises")
webexercises::add_to_quarto()
```

This will add the following:

A `webex.css` and `webex.js` in an include directory.
For a nice MCQ presentation i change the `.webex-radiogroup label` in `webex.css` to:

```{bash, eval=FALSE}
.webex-radiogroup label {
  /*Text colour*/
  color: : #aaaaaa;
  margin-left: 2em;
  margin-bottom: 0.25em;
  text-indent: -1em;
  padding-left: 0.5em;
  font-weight: 400;
  display: block;
  /*Set border of text to solid and dark grey*/
  border: 2px solid #808080;
  border-radius: 0.25em;
}
```

Additionally, a `webexercises.qmd` file is created.
This contains examples of the various different quizzes.
I delete this.